Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-19 Manuscript/FLPhish(Trans).tex
FLPhish manuscript update

\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data. Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using their gradient model updates. In each iteration of FL, the central server sends a model to each client. The client uses its private data to update the model and sends the model gradient update back to the central server. Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model. Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregation process. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks for some designed attacks can still bypass the defense \cite{ref_06_model}. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}

@@

In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it. We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference tp determine a client's level of trust. We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance. At last, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment demonstrates the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL. 
\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.

>>>>

\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data. Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using model updates from distributed clients. In each iteration of FL, the central server sends a model to each client. The client uses its private data to update the model and sends the model gradient update back to the central server. Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model. Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregation process. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL. Our contributions are four-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}

@@

In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it. We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust. We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance. At last, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment demonstrates the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL. 
\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.
